### 2018-04-30 paper/file-exchange-design.tex
yaaaay, outline figure
removed unbound references to article

\subsection{Scheduling and transferring a file}%
\label{file-transfer}

@@

As stated above, Alice and Bob exchange some limited data out-of-bound using 
their smartphones.
The information they will exchange is the following:
\begin{enumerate}
  \item Bob creates an onion route header, \(H_\rdv\), by running 
    \(\SPOR[\Recv]\) (\cref{SPORRecv}) and gives it to Alice.
  \item Alice gives Bob number of file chunks, \(n\), and the size of the file 
    chunks.
  \item They agree on a file-specific key \(k\) for some (authenticated) 
    encryption scheme \(\Enc*\).
\end{enumerate}
Then Alice encrypts the file \(f\) and receives the ciphertext \(c_f\gets 
  \Enc*[Enc](k, f)\).
She then divides \(c_f\) into \(n\) chunks, \(c_f^{(1)}, \dotsc, c_f^{(n)}\), 
and runs \(\SPOR[\Send](H_\rdv, c_f^{(i)})\) for all \(1\leq i\leq n\) in 
parallel.
\commentDaniel{Or shall we do it sequentially?}

>>>>

\subsection{Scheduling and transferring a file}%
\label{sec:file_exchange}

@@

As stated above, Alice and Bob exchange some limited data out-of-bound using 
their smartphones.
The information they will exchange is the following:
\begin{enumerate}
  \item Bob creates an onion route header, \(H_\rdv\), by running 
    \([\Recv]\) %(\cref{SPORRecv}) 
    and gives it to Alice.
  \item Alice gives Bob number of file chunks, \(n\), and the size of the file 
    chunks.
  \item They agree on a file-specific key \(k\) for some (authenticated) 
    encryption scheme \(\Enc*\).
\end{enumerate}
Then Alice encrypts the file \(f\) and receives the ciphertext \(c_f\gets 
  \Enc*[Enc](k, f)\).
She then divides \(c_f\) into \(n\) chunks, \(c_f^{(1)}, \dotsc, c_f^{(n)}\), 
and runs \([\Send](H_\rdv, c_f^{(i)})\) for all \(1\leq i\leq n\) in 
parallel.
\commentDaniel{Or shall we do it sequentially?}

### 2018-04-30 paper/message-passing-design.tex
removed unbound references to article

\begin{figure}[t]
  %\framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}[1]
    %\Require{$\pk, \sk$ is the public--private key-pair of the node.}
    \Function{\SPOR[\Fwd]}{$C_H, m$}
      \State $H\gets \DeBEdec[\mpk, \sk, C_H]$
      \If{$H = \bot$}
        \State \Return $\bot$
      \EndIf
      \State $\{d_i\}\concat C_H'\gets H$
      \If{$C_H' = \top$}
        \State \Return $\Store[m]$
      \EndIf
      \For{$d\in \{d_i\}$}
        \Comment{Uniformly randomly chosen}
        \If{$d\method \Fwd[C_H', m] \neq \bot$}
          \State \Return $\top$
        \EndIf
      \EndFor
      \State \Return $\bot$
    \EndFunction
  \end{algorithmic}

  \begin{algorithmic}[1]
    \Function{\Store}{$m$}
      \State $m\gets \DeBEdec[\mpk, \sk, c_m]$
      \If{$m = \bot$}
        \State \Return $\bot$
      \EndIf
      \State Store $m$ to disk.
      \State \Return $\top$
    \EndFunction
  \end{algorithmic}
  %\end{minipage}}
  \caption{\label{SPORFwd}%
    The \(\SPOR[\Fwd]\) algorithm forwards \(m\) down the route \(H\), obtained 
    by decrypting \(C_H\) with the node's associated private key.
    The special value \(H = \top\) indicated the end of the route, thus \(c_m\) 
    is intended for the local node and \(c_m\) is instead sent to disk using 
    \(\Store\) (\cref{SPORRecv}).%
  }
\end{figure}

For instance, if Alice wants to send a message \(m\) to Bob, they are both going to perform a part of the building algorithm.
Bob uses the \(\SPOR[\Recv]\) function (See \cref{SPORRecv}) to create a probabilistic onion route $\mathcal{H_B}$ from
 a rendez-vous (RV) layer $\mathcal{L_{RV}}$ to its own devices from its \squad---all the hops on the route are 
chosen by Bob uniformly at random from the Global Overlay.
 \(\SPOR[\Recv]\)
returns $\mathcal{H_B}$ and  that Bob gives to Alice using an
out-of-band channel, \eg using one device of its \squad.
PORs have \(L\) layers, and for each layer the number of
alternatives nodes depends of a failure threshold \(\theta\). 
As long as \(\theta\) is not exceeded, alternatives nodes are added in
\(H_\rdv\) as depicted in \cref{ExtendRoute}. Thus the probability of
failure for the extension is \(1 - (1 - \theta)^L\).

Once Alice get the \(H_\rdv\), Alice uses \(\SPOR[\Send]\) at some
later time to send the message to Bob using any of her devices from
its \squad (See \cref{SPORSend}). First, \(\SPOR[\Send]\) extends the route
\(H_\rdv\) with some hops of Alice's choosing (uniformly randomly
chosen). Second, \(\SPOR[\Send]\) extracts from the onion the first
layer, which contained the overall
possible rendez-vous points $D$ previously selected by the recipient (i.e. Bob).
One device from $D$ is randomly chosen, and the \(\SPOR[\Fwd]\)
sub-function is called as long as the message forwarding to one node of
the next layer is not successful (See \cref{SPORFwd}). Along the path, each node decrypts
in sequence the different layer with the current node’s private key. 
The end of the route is reached when special value \(H_\rdv = \top\) is
encountered. Consequently the ciphered message \(c_m\) is then stored
in the disk of the local node through the \(\Store\) sub function 
(\cref{SPORRecv}).

@@

>>>>

Once Alice get the \(H_\rdv\), Alice uses \([\Send]\) at some
later time to send the message to Bob using any of her devices from
its \squad.% (See \cref{SPORSend}). 
First, \([\Send]\) extends the route
\(H_\rdv\) with some hops of Alice's choosing (uniformly randomly
chosen). Second, \([\Send]\) extracts from the onion the first
layer, which contained the overall
possible rendez-vous points $D$ previously selected by the recipient (i.e. Bob).
One device from $D$ is randomly chosen, and the \([\Fwd]\)
sub-function is called as long as the message forwarding to one node of
the next layer is not successful.% (See \cref{SPORFwd}). 
Along the path, each node decrypts
in sequence the different layer with the current node’s private key. 
The end of the route is reached when special value \(H_\rdv = \top\) is
encountered. Consequently the ciphered message \(c_m\) is then stored
in the disk of the local node through the \(\Store\) sub function.%(\cref{SPORRecv}).

@@

\begin{figure}[t]
  %\framebox{\begin{minipage}{0.96\linewidth}
  \begin{algorithmic}[1]
    %\Require{$\pk, \sk$ is the public--private key-pair of the node.}
    \Function{[\Fwd]}{$C_H, m$}
      \State $H\gets \DeBEdec[\mpk, \sk, C_H]$
      \If{$H = \bot$}
        \State \Return $\bot$
      \EndIf
      \State $\{d_i\}\concat C_H'\gets H$
      \If{$C_H' = \top$}
        \State \Return $\Store[m]$
      \EndIf
      \For{$d\in \{d_i\}$}
        \Comment{Uniformly randomly chosen}
        \If{$d\method \Fwd[C_H', m] \neq \bot$}
          \State \Return $\top$
        \EndIf
      \EndFor
      \State \Return $\bot$
    \EndFunction
  \end{algorithmic}

  \begin{algorithmic}[1]
    \Function{\Store}{$m$}
      \State $m\gets \DeBEdec[\mpk, \sk, c_m]$
      \If{$m = \bot$}
        \State \Return $\bot$
      \EndIf
      \State Store $m$ to disk.
      \State \Return $\top$
    \EndFunction
  \end{algorithmic}
  %\end{minipage}}
  \caption{\label{SPORFwd}%
    The \([\Fwd]\) algorithm forwards \(m\) down the route \(H\), obtained 
    by decrypting \(C_H\) with the node's associated private key.
    The special value \(H = \top\) indicated the end of the route, thus \(c_m\) 
    is intended for the local node and \(c_m\) is instead sent to disk using 
    \(\Store\).% (\cref{SPORRecv}).%
  }
\end{figure}

% For instance, if Alice wants to send a message \(m\) to Bob, they are both going to perform a part of the building algorithm.
% Bob uses the \([\Recv]\) function (See \cref{SPORRecv}) to create a probabilistic onion route $\mathcal{H_B}$ from
%  a rendez-vous (RV) layer $\mathcal{L_{RV}}$ to its own devices from its \squad---all the hops on the route are 
% chosen by Bob uniformly at random from the Global Overlay.
%  \(\SPOR[\Recv]\)
% returns $\mathcal{H_B}$ and  that Bob gives to Alice using an
% out-of-band channel, \eg using one device of its \squad.
% PORs have \(L\) layers, and for each layer the number of
% alternatives nodes depends of a failure threshold \(\theta\). 
% As long as \(\theta\) is not exceeded, alternatives nodes are added in
% \(H_\rdv\) as depicted in \cref{ExtendRoute}. Thus the probability of
% failure for the extension is \(1 - (1 - \theta)^L\).

% Once Alice get the \(H_\rdv\), Alice uses \(\SPOR[\Send]\) at some
% later time to send the message to Bob using any of her devices from
% its \squad (See \cref{SPORSend}). First, \(\SPOR[\Send]\) extends the route
% \(H_\rdv\) with some hops of Alice's choosing (uniformly randomly
% chosen). Second, \(\SPOR[\Send]\) extracts from the onion the first
% layer, which contained the overall
% possible rendez-vous points $D$ previously selected by the recipient (i.e. Bob).
% One device from $D$ is randomly chosen, and the \(\SPOR[\Fwd]\)
% sub-function is called as long as the message forwarding to one node of
% the next layer is not successful (See \cref{SPORFwd}). Along the path, each node decrypts
% in sequence the different layer with the current node’s private key. 
% The end of the route is reached when special value \(H_\rdv = \top\) is
% encountered. Consequently the ciphered message \(c_m\) is then stored
% in the disk of the local node through the \(\Store\) sub function 
% (\cref{SPORRecv}).
